Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
Improved the RQs a bit

\SubSection{Research Question(s)}
One clear main research question
RQ 1 - In which situations should companies expect MDD to be successfully adopted?

>>>>

\SubSection{Research Questions}
\begin{itemize}
\item \textbf{RQ1:} In which situations should companies expect that changing to MDSD would lead to positive effects? 
\item \textbf{RQ1.1:} In which domain(s) is MDSD the most successful? 
\item \textbf{RQ1.2:} Which software development process(es) has been most successfully used in conjunction with MDSD?
\item \textbf{RQ1.3:} What are the characteristics of the systems of the companies that successfully use MDSD?
\end{itemize}

\begin{itemize}
\item They are probably not worded optimally... Here're some alturnutuves:
\item In which situations should companies expect MDD to be successfully adopted?
\item In which situations should companies expect that the adoption of MDD would lead to a performance boost?
\end{itemize}
